Data for the Ontario Restaurant Closures Experiment

### 2021-02-20 outputs/paper/data_simulation.Rmd

```{r, warning = FALSE}
# read in the data
# NOTE: scripts 01_scrape_health_depts, 04_clean_restaurant_list_csvs, and 02_sampling_frame must have been run already

table_for_surveys <- read_csv(here::here("outputs/table_for_surveys.csv"))

@@

@@

@@

## Survey 1
```{r, warning = FALSE}
set.seed(19)
survey_1 <- survey_1 %>%
  mutate(service_type = sample(x = c("dinein",
                                     "both",
                                     "takeout"),
      size = num_total,
      replace = TRUE, 
      prob = c(0.06, 0.615, 0.325)
      ))

@@

## Survey 2
```{r, warning = FALSE}
set.seed(19)
survey_2 <- survey_2 %>%
  mutate(service_type = sample(x = c("dinein",
                                     "both",
                                     "takeout"),
      size = num_total,
      replace = TRUE, 
      prob = c(0.06, 0.615, 0.325)
      ))

@@

## Survey 1
```{r, warning = FALSE}
set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(disability = sample(c("yes", "no", "nonanswer"),
                             size = num_total,
                             prob = c(0.005, .985, 0.01),
                             replace = TRUE))

@@

## Survey 2
```{r, warning = FALSE}
set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(disability = sample(c("yes", "no", "nonanswer"),
                             size = num_total,
                             prob = c(0.005, .985, 0.01),
                             replace = TRUE))

@@

```{r, warning = FALSE}
### Load census dataset by Health Regions ###
### Download link: https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/details/download-telecharger/comp/GetFile.cfm?Lang=E&FILETYPE=CSV&GEONO=058 ###
census_2016 <- read.csv(here("inputs", "data", "census_2016.csv"))
census_2016 <- janitor::clean_names(census_2016)

@@

### Get data from the randomly selected Health Regions ###
# GEO_CODE indicates public health regions, taken from Census 2016 links:
#https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/search-recherche/lst/results-resultats.cfm?Lang=E&TABID=1&G=1&Geo1=&Code1=&Geo2=&Code2=&GEOCODE=35&type=0

@@

northwest <- get_region_data(3549)
# southwestern <- get_region_data(3502)
# Southwestern is a newer health unit. it was created by almagamating oxford and elgin-st. thomas units:
oxford <- get_region_data(3552)
elgin <- get_region_data(3531)
waterloo <- get_region_data(3565)
durham <- get_region_data(3530)
sudbury <- get_region_data(3561)
brant <- get_region_data(3527)

@@

get_pop_info <- function(x){
  c(as.numeric(x$dim_sex_3_member_id_1_total_sex[x$dim_profile_of_health_regions_2247 == "Population, 2016"]),
    as.numeric(x$dim_sex_3_member_id_1_total_sex[x$dim_profile_of_health_regions_2247 == "Aboriginal identity"]),
    as.numeric(x$dim_sex_3_member_id_1_total_sex[x$dim_profile_of_health_regions_2247 == "Total visible minority population"]),
    as.numeric(x$dim_sex_3_member_id_1_total_sex[x$dim_profile_of_health_regions_2247 == "72 Accommodation and food services"]),
    as.numeric(x$dim_sex_3_member_id_3_female[x$dim_profile_of_health_regions_2247 == "Total - Age groups and average age of the population - 100% data"]))
}

@@

```{r, warning = FALSE}
populations_split <- matrix(ncol=4, nrow=5)
populations_split[,1] <- c("Total_Population", "Indigenous_Population_25%_sample", "Visible_Minority_25%_sample", "Accommodation_and_Food_Services_25%_sample", "Total_Population_Women")
populations_split[,2] <- ontario_pop

@@

```{r, warning = FALSE}
### Get percentage proportions of demographic groups of interest ###

@@

## Survey 1
```{r, warning = FALSE}
set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(woman = sample(c("yes","no","nonanswer"), size = num_total, prob = c(0.154, 0.836, 0.01), replace = TRUE))

@@

```{r, warning = FALSE}
set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(woman = sample(c("yes","no","nonanswer"), size = num_total, prob = c(0.154, 0.836, 0.01), replace = TRUE))

@@

```{r, warning = FALSE}
set.seed(19893)
survey_2 <- bind_rows(
  survey_2 %>%
    filter(group == "treatment") %>%
    mutate(shutdown = sample(c("none", "temporary", "permanent"), 
                                                            size = num_treat, 
                                                            prob = c(0.558, 0.432, 0.01),
                                                            replace = TRUE))
  ,
  survey_2 %>%
    filter(group == "control") %>%
    mutate(shutdown = sample(c("none", "temporary", "permanent"), 
                                                          size = num_control, 
                                                          prob = c(.99, 0.005, 0.005),
                                                          replace = TRUE))
) %>%
  arrange(ID)

@@

```{r, warning = FALSE}
set.seed(19894)
survey_1 <- survey_1 %>%
  mutate(revenue = 62963 * rf(num_total,20,20))

@@

```{r, warning = FALSE}
set.seed(19894)
survey_2 <- survey_2 %>%
  mutate(revenue = 62963 * rf(num_total,20,20)) %>%
  mutate(factor = abs(rnorm(num_total, 1, .1))) %>%
  mutate(revenue = factor * revenue) %>%
  select(-factor)

@@

@@

@@

2.4 FTE -> 1.9 FT + 1 PT.
0.79 = 1.9 / 2.4 = 1.9 / (1.9 + 0.5)
0.42 = 1 / 2.4 = 0.42 = 1 / (1.9 + 0.5)

## Survey 1
```{r, warning = FALSE}
set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(fte = revenue / 6833) %>%
  mutate(ft = round(fte * 0.79)) %>%
  mutate(pt = round(fte * 0.42)) %>%
  select(-fte)

@@

For the second survey, we will assume that treatment restaurants shifted towards part time random amounts-- that is, the number of full time employees per part time employee dropped from 1.9. X is some number less than or equal to 1.9.
x / (x + 0.5)
1 / (x + 0.5)

```{r, warning = FALSE}
set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(fte = revenue / 6833) %>%
  mutate(ptincrease = 1.9 * (1 - abs(rnorm(num_total, 0, sd = 0.1)))) %>%
  mutate(ft = round(fte * (ptincrease / (ptincrease + 0.5)))) %>%
  mutate(pt = round(fte * (1 / (ptincrease + 0.5)))) %>%
  select(-fte, - ptincrease)

@@

```{r, warning = FALSE}
num_cols_1 = 11

@@

```{r, warning = FALSE}
num_cols_2 = 12

@@

```{r, warning = FALSE}
write_csv(survey_1, here("outputs/data/survey_1.csv"))
write_csv(survey_2, here("outputs/data/survey_2.csv"))
```

>>>>

Analysis for this project uses the R statistical programming language [@R], and more specifically, the `tidyverse` package for data manipulation [@tidyverse]. Because the data is managed using R Projects, `here` is used to reference file locations [@here]. `kableExtra` formats tables [@kableExtra]. `bookdown` is used to format the report [@bookdown].

First, we read in the skeleton for the survey data. This is what we would hypothetically know about a restaurant before they took the survey. We keep only the ID numbers, the group, and the last 3 characters of the postal code, which the survey-taker will have to enter to verify identity. All other variables, like name and full address, are only kept in the only frame for surveying, which contains no private information.

```{r, warning = FALSE}
# read in the data
# NOTE: scripts 01_scrape_health_depts, 
# 02_stratified_cluster_sampling,
# 03_clean_restaurant_list_csvs, 
# 04_restaurant_survey_frame,
# and 05_import_yelp_data must have been run already

table_for_surveys <- read_csv(here::here("outputs/data/table_for_surveys.csv"))

@@

From there, data was simulated for all questions asked on the survey.

@@

First, some research:

@@

## Survey 1
```{r, warning = FALSE}
# randomly assign service_provided using ratios above

set.seed(19)
survey_1 <- survey_1 %>%
  mutate(service_type = sample(x = c("dinein",
                                     "both",
                                     "takeout"),
      size = num_total,
      replace = TRUE, 
      prob = c(0.06, 0.615, 0.325)
      ))

@@

## Survey 2
```{r, warning = FALSE}
# randomly assign service_provided using ratios above

set.seed(19)
survey_2 <- survey_2 %>%
  mutate(service_type = sample(x = c("dinein",
                                     "both",
                                     "takeout"),
      size = num_total,
      replace = TRUE, 
      prob = c(0.06, 0.615, 0.325)
      ))

@@

## Survey 1
```{r, warning = FALSE}
# randomly assign disability status using ratios above

set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(disability = sample(c("yes", "no", "nonanswer"),
                             size = num_total,
                             prob = c(0.005, .985, 0.01),
                             replace = TRUE))

@@

## Survey 2
```{r, warning = FALSE}
# randomly assign disability status using ratios above

set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(disability = sample(c("yes", "no", "nonanswer"),
                             size = num_total,
                             prob = c(0.005, .985, 0.01),
                             replace = TRUE))

@@

Some research for racial and ethnic minorities and women in Canada and in business:

```{r, warning = FALSE}
### Load census dataset by Health Regions ###
### Download link: 
### https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/details/
### download-telecharger/comp/GetFile.cfm?Lang=E&FILETYPE=CSV&GEONO=058
census_2016 <- read.csv(here("inputs", "data", "census_2016.csv"))
census_2016 <- janitor::clean_names(census_2016)

@@

### Get data from the randomly selected Health Regions ###
# GEO_CODE indicates public health regions, taken from Census 2016 links:
# https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/
# search-recherche/lst/results-resultats.cfm?Lang=E&TABID=1&G=1&Geo1=&Code1=
# &Geo2=&Code2=&GEOCODE=35&type=0

@@

northwest <- get_region_data(3549)
# Southwestern was created by almagamating oxford and elgin-st. thomas units:
oxford <- get_region_data(3552)
elgin <- get_region_data(3531)
waterloo <- get_region_data(3565)
durham <- get_region_data(3530)
sudbury <- get_region_data(3561)
brant <- get_region_data(3527)

@@

get_pop_info <- function(x){
  c(as.numeric(x$dim_sex_3_member_id_1_total_sex
               [x$dim_profile_of_health_regions_2247 == "Population, 2016"]),
    as.numeric(x$dim_sex_3_member_id_1_total_sex
               [x$dim_profile_of_health_regions_2247 == "Aboriginal identity"]),
    as.numeric(x$dim_sex_3_member_id_1_total_sex
               [x$dim_profile_of_health_regions_2247 == 
                   "Total visible minority population"]),
    as.numeric(x$dim_sex_3_member_id_1_total_sex
               [x$dim_profile_of_health_regions_2247 == 
                   "72 Accommodation and food services"]),
    as.numeric(x$dim_sex_3_member_id_3_female
               [x$dim_profile_of_health_regions_2247 == 
                   "Total - Age groups and average age of the population - 100% data"]))
}

@@

```{r, warning = FALSE}
# Split the population info into our treatment and control groups.

populations_split <- matrix(ncol=4, nrow=5)
populations_split[,1] <- c("Total_Population", 
                           "Indigenous_Population_25%_sample", 
                           "Visible_Minority_25%_sample", "
                           Accommodation_and_Food_Services_25%_sample", 
                           "Total_Population_Women")
populations_split[,2] <- ontario_pop

@@

```{r, warning = FALSE}
### Get percentage proportions of demographic groups of interest

@@

## Survey 1
```{r, warning = FALSE}
# Randomly assign racial and ethnic minorities, and women, using the ratios above:

set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(woman = sample(c("yes","no","nonanswer"), 
                        size = num_total, 
                        prob = c(0.154, 0.836, 0.01), 
                        replace = TRUE))

@@

```{r, warning = FALSE}
# Randomly assign racial and ethnic minorities, and women, using the ratios above:

set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(woman = sample(c("yes","no","nonanswer"), 
                        size = num_total, 
                        prob = c(0.154, 0.836, 0.01), 
                        replace = TRUE))

@@

```{r, warning = FALSE}
# Randomly assign shutdown using the ratios above only for the treatment group:

set.seed(19893)
survey_2 <- bind_rows(
  survey_2 %>%
    filter(group == "treatment") %>%
    mutate(shutdown = sample(c("none", "temporary", "permanent"),
                             size = num_treat,
                             prob = c(0.558, 0.432, 0.01),
                             replace = TRUE))
  ,
  survey_2 %>%
    filter(group == "control") %>%
    mutate(shutdown = sample(c("none", "temporary", "permanent"),
                             size = num_control,
                             prob = c(.99, 0.005, 0.005),
                             replace = TRUE))
) %>%
  arrange(ID)

@@

```{r, warning = FALSE}
# Randomly sample from the scaled F distribution to generate restaurant revenues:

set.seed(19894)
survey_1 <- survey_1 %>%
  mutate(revenue = 62963 * rf(num_total,20,20))

@@

```{r, warning = FALSE}
# Randomly sample from the scaled F distribution to generate restaurant revenues, and apply a random number around 1 to add variation:

set.seed(19894)
survey_2 <- survey_2 %>%
  mutate(revenue = 62963 * rf(num_total,20,20)) %>%
  mutate(factor = abs(rnorm(num_total, 1, .1))) %>%
  mutate(revenue = factor * revenue) %>%
  select(-factor)

# Reduce the treatment revenues to those that shutdown:

@@

# reduce the treatment revenues for those with more dine-in and less take-out service:

@@

# reduce the treatment revenues further for racial and ethnic minority owned businesses:

@@

2.4 FTE -> 1.9 FT + 1 PT.

$ 1.9 / (1.9 + 0.5) = 1.9 / 2.4 = 0.79 $

$ 1 / (1.9 + 0.5) = 1 / 2.4 = 0.42 $

## Survey 1
```{r, warning = FALSE}
# Use revenue to generate realistic numbers of employees for restaurants:

set.seed(19893)
survey_1 <- survey_1 %>%
  mutate(fte = revenue / 6833) %>%
  mutate(ft = round(fte * 0.79)) %>%
  mutate(pt = round(fte * 0.42)) %>%
  select(-fte)

@@

For the second survey, we will assume that treatment restaurants shifted towards part time random amounts-- that is, the number of full time employees per part time employee dropped from 1.9. X is some number less than or equal to 1.9.

```{r, warning = FALSE}
# Use revenue to generate realistic numbers of employees for restaurants:

set.seed(19893)
survey_2 <- survey_2 %>%
  mutate(fte = revenue / 6833) %>%
  mutate(ptincrease = 1.9 * (1 - abs(rnorm(num_total, 0, sd = 0.1)))) %>%
  mutate(ft = round(fte * (ptincrease / (ptincrease + 0.5)))) %>%
  mutate(pt = round(fte * (1 / (ptincrease + 0.5)))) %>%
  select(-fte, - ptincrease)

@@

```{r, warning = FALSE}
# Randomly select only a subset of all the generated responses to keep, simulating nonresponse:
# Also randomly select columns to delete in partial responses, and delete the data from those rows/columns:

num_cols_1 = 11

@@

```{r, warning = FALSE}
# Randomly select only a subset of all the generated responses to keep, simulating nonresponse:
# Also randomly select columns to delete in partial responses, and delete the data from those rows/columns:

num_cols_2 = 12

@@

```{r, warning = FALSE}
# Save the two survey results tables:

write_csv(survey_1, here("outputs/data/survey_1.csv"))

write_csv(survey_2, here("outputs/data/survey_2.csv"))
```
